Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-05-03 Paper Sigatoka - 2015.tex
d2

\usepackage{soul}
\usepackage{marginnote}
\usepackage{float}
\usepackage{natbib}
\usepackage{hyperref}

@@

This disease attacks the plant leaves producing a rapid deterioration
of the leaf area, affects the growth and productivity of the plants
due to the impairment of their photosinthetic ability, causes a
reduction in the quality of the fruit, and promotes premature
maturation \marginnote{maturation or ripening?} of bunches, which is
the major cause of product losses associated with the black
Sigatoka. \figurename~\ref{fig:diseasestages} shows three stages of
this disease.

>>>>

\usepackage{soul}
\usepackage{marginnote}
\usepackage{float}
\usepackage{hyperref}

@@

This disease attacks the plant leaves producing a rapid deterioration
of the leaf area, affects the growth and productivity of the plants
due to the impairment of their photosinthetic ability, causes a
reduction in the quality of the fruit, and promotes premature
ripening of bunches, which is
the major cause of product losses associated with the black
Sigatoka. \figurename~\ref{fig:diseasestages} shows three stages of
this disease.
